---
title: "Title"
author: "Nick J Lyon"
format: 
  revealjs: 
    slide-number: c
    incremental: true
    scrollable: false
    theme: [night, slides.scss]
    reference-location: document
    footer: "[Programming in R for Biologists](https://njlyon0.github.io/teach_r-for-bio/)"
---

## [Incremental List]{.blue}
 
Incremental because of [presentation]{.purple}-level YAML 

- [X]{.orange}
- [Y]{.pink}
- [Z]{.gold}

## Non-Incremental List

:::{.nonincremental}

- A
- B
- C

:::

## Multi-Column Slide

:::: {.columns}

::: {.column width="33.33%"}
contents...
:::

::: {.column width="33.33%"}
contents...
:::

::: {.column width="33.33%"}
contents...
:::

::::

## Slide with Aside

:::{.nonincremental}

- x
- y
- z\*

:::

::: aside
\* = footnote (smaller/lighter text)
:::

## Example Code Chunk

Including incremental line emphasis

```{.r code-line-numbers="|2|5"}
# Make vector
vec <- c(1, 2, 3)

# Take average
mean(vec)
```

## Executable Code Chunk

```{r}
#| echo: true
#| output-location: fragment

# Make vector
vec <- c(1, 2, 3)

# Take average
mean(vec)
```

## Code Chunk Outputting to Next Slide

```{r}
#| echo: true
#| output-location: slide

# Load ggplot2
library(ggplot2)

# Create plot
ggplot(airquality, aes(x = Temp, y = Ozone)) +
  geom_point() +
  geom_smooth(method = "loess")
```

## Slide with different background color {background-color="#FFB02F"} 

Hello world
